### 2018-08-06 paper/squad-overlay-design.tex
done with III.E.2

Devices need to know the address of SPORES participants in order to craft PORs.
To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007} among all nodes in SPORES. \commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} for \textbf{secure} RPS}.
It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view}). 
The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
Finally, offline nodes are quickly evicted from devices' views.

@@

In SPORES, a descriptor for $d$ contains the following information:
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(P_d\) is the node's probability of remaining online at the time of the descriptor's creation.
\end{itemize}

@@

>>>>

\newcommand\rpsview{\ensuremath{\mathcal{V}}\xspace}
\newcommand\desc{\ensuremath{{\mathtt{desc}}}\xspace}

Devices need to know the address of SPORES participants in order to craft PORs.
To this end, we employ a Random Peer Sampling service~\cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007} among all nodes in SPORES. \commentAL{TODO: cite \cite{Jesi_Montresor_van_Steen_2010} for \textbf{secure} RPS}.
It is a gossip protocol that allows each participant to keep a fixed-size \emph{random} subset of other nodes' descriptor (that we will call the \emph{view} \rpsview). 
The view is constantly evolving, as queries are periodically issued between nodes to exchange descriptors between their respective views.
Finally, offline nodes are quickly evicted from devices' views.

@@

In SPORES, a descriptor $\desc_d$ describing device $d$ contains the following information:
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(P_d\) is the node's probability of remaining online at the time of the descriptor's creation.
\end{itemize}

@@

\newcommand\layer{\ensuremath{{\mathcal{L}}}\xspace}
\newcommand\Poff{\ensuremath{P_{\text{off}}}\xspace}

Routes are created via Sphinxes, as described in section~\ref{SPOR}.
Each layer \layer constituting the route is created by the same \CreateLayer\xspace function.

In \name, we wish to maximize the availability of the route.
Therefore, each layer \layer is created so as to reach the availability threshold $\theta$, a parameter chosen by the user.
Note that Sphinxes is agnostic to this use-case: one could want to maximize other characteristics, e.g. the layer's expected bandwidth.

\CreateLayer\xspace iteratively adds random descriptors from the RPS's view \rpsview to the current layer \layer, until the layer's probability of being offline, $\Poff^\layer$, falls below the availability threshold $\theta$:

$$ \Poff^\layer = \sum\limits_{d \in \layer}\desc_d.P_d $$

Recall that each layer in Sphinxes has a constant number of nodes $w_\layer$, that is a Sphinxes parameter.
If $w_\layer$ is reached before $\Poff^\layer < \theta$, then we early abort \CreateLayer.
On the other hand, if $|\layer| < w_\layer$, we pad the layer with blank descriptors, such that the header always weighs the same size.
